Forecasting the 2024 US Presidential Election

### 2024-11-03 paper/paper.qmd
Minor fixes in pdf output

## Appendix A: Pollster Methodology Overview
Emerson College Polling was initially a college polling exercise, and is now an "innovative, nationally-ranked" non-partisan polling center (@AboutUs). For the 2024 USA Presidential Election pollster, the Emerson College Polling defined the population to be "likely voters" of 2024 United States Presidential Election. Emerson College Polling does indicate that the targeted population of "likely voters" is based on "2024 Likely Voter Modeling." However, the methodology for this modelling and the specific model is not indicated, so the specific validity of the targeted population cannot be determine (@Polling).

@@

## Appendix B: Idealized Survey Design for $100K Budget

## Introduction

@@

## Sampling Approach

@@

## Respondent Recruitment

@@

## Data Validation

@@

## Poll Aggregation

@@

## Copy of Survey

>>>>

## Appendix A: Pollster Methodology Overview {-}
Emerson College Polling was initially a college polling exercise, and is now an "innovative, nationally-ranked" non-partisan polling center (@AboutUs). For the 2024 USA Presidential Election pollster, the Emerson College Polling defined the population to be "likely voters" of 2024 United States Presidential Election. Emerson College Polling does indicate that the targeted population of "likely voters" is based on "2024 Likely Voter Modeling." However, the methodology for this modelling and the specific model is not indicated, so the specific validity of the targeted population cannot be determine (@Polling).

@@

## Appendix B: Idealized Survey Design for $100K Budget {-}

## Introduction {-}

@@

## Sampling Approach {-}

@@

## Respondent Recruitment {-}

@@

## Data Validation {-}

@@

## Poll Aggregation {-}

@@

## Copy of Survey {-}
